An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-12 EconGrowth.Rnw
Now generating single-factor parameter graphs for all models within the text.

#############################
# Creates a graph with confidene intervals for the single-factor model for the given factor
##
createSFParamsGraph <- function(factor){
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda or m), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRowsForParamsGraph, factor=factor))
print(dataTable)
#   graph <- segplot(country ~ upperCI + lowerCI | parameter, 
#                    data = dataTable, 
#                    centers = value, #identifies where the dots should be placed
#                    draw.bands = FALSE, #provides nicer error bars
#                    horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
#                    layout = c(2,1), #2 column, 1 row
#                    index.cond = list(c(1,2)), #orders the panels as lambda, m
#                    #set labels and bg color in strip
#                    strip = strip.custom(factor.levels=c("$\\lambda$", "$m"),  
#                                         bg="white"),
#                    col = "black", #Sets line color to black
#                    lwd = 1, #Sets line width to 1.0
#                    ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
#                    scales = list(cex=scaleTextSize, #controls text size on scales.
#                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
#                                  x=list(cex=0.75), #reduces text size so that country abbrevs are legible
#                                  y=list(relation="free", #allow each axis to be different
#                                         at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
#                                                 c(0.0, 0.5, 1.0)
#                                         )
#                                  )
#                    )
#   )  
  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable,
                   centers = value, #identifies where the dots should be placed
                   draw.bands = FALSE, #provides nicer error bars
                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
                   layout = c(2,1), #2 column, 1 row
                   col = "black", #Sets line color to black
                   lwd = 1, #Sets line width to 1.0
                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", "$m$")),
                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
                   scales = list(cex=scaleTextSize, #controls text size on scales.
                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
                                 y=list(relation="free", #allow each axis to be different
                                        at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
                                                c(0.0, 0.5, 1.0)
                                                )
                                        )
                                 )
                   )

  return(graph)
}

createSFParamsGraph("L")

@@

>>>>

#############################
# Creates a graph with confidene intervals for the single-factor model for the given factor
##
createSFParamsGraph <- function(factor){
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda or m), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRowsForParamsGraph, factor=factor))
  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable,
                   centers = value, #identifies where the dots should be placed
                   draw.bands = FALSE, #provides nicer error bars
                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
                   layout = c(2,1), #2 column, 1 row
                   col = "black", #Sets line color to black
                   lwd = 1, #Sets line width to 1.0
                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", "$m$")),
                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
                   scales = list(cex=scaleTextSize, #controls text size on scales.
                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
                                 y=list(relation="free", #allow each axis to be different
                                        at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
                                                c(0.0, 0.5, 1.0)
                                                )
                                        )
                                 )
                   )

  return(graph)
}
@

@@

<<SFk_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
createSFParamsGraph("K")
@

<<SFl_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
createSFParamsGraph("L")
@

<<SFq_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
createSFParamsGraph("Q")
@

<<SFx_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
createSFParamsGraph("X")
@

<<SFu_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
createSFParamsGraph("U")
@
